Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2017-01-06 Papers/2017/LogicaUniversalis-HajekAndersonControversy/main.tex
Remove redundant sentence

\section{Introduction}
We present an exemplary study in \emph{Computational Metaphysics},
which is an emerging, interdisciplinary field aiming at the rigorous
formalisation and deep logical assessment of rational, philosophical
arguments on the computer.  The particular focus here is on the
ontological argument for the existence of God.  While related work
\citep{oppenheimer11,rushby13} has concentrated on Anselm's simpler original
version of the ontological argument and formalized it in classical
predicate logic, we here focus on modern variants of it requiring
higher-order modal logic. More precisely, the variants studied here are
all emendations of Kurt Gödel's seminal contribution
\citep{GoedelNotes}, respectively, Dana Scott's variant of it
\cite{ScottNotes} (cf. Fig.~\ref{fig:Goedel}).

>>>>

\section{Introduction}
We present an exemplary study in \emph{Computational Metaphysics},
which is an emerging, interdisciplinary field aiming at the rigorous
formalisation and deep logical assessment of rational, philosophical
arguments on the computer.  The particular focus here is on the
ontological argument for the existence of God.  While related work
\citep{oppenheimer11,rushby13} has concentrated on Anselm's simpler original
version of the ontological argument and formalized it in classical
predicate logic, we here focus on modern variants of Kurt Gödel's seminal contribution
\citep{GoedelNotes} requiring
higher-order modal logic.

% More precisely, the variants studied here are
% all emendations of Dana Scott's variant
% \cite{ScottNotes} (cf. Fig.~\ref{fig:Goedel}).
